---
title: Bioc 2015 GoogleGenomics Workshop
output:
  BiocStyle::html_document
---

<!-- Copyright 2015 Google Inc. All rights reserved. -->

<!-- Licensed under the Apache License, Version 2.0 (the "License"); -->
<!-- you may not use this file except in compliance with the License. -->
<!-- You may obtain a copy of the License at -->

<!--     http://www.apache.org/licenses/LICENSE-2.0 -->

<!-- Unless required by applicable law or agreed to in writing, software -->
<!-- distributed under the License is distributed on an "AS IS" BASIS, -->
<!-- WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied. -->
<!-- See the License for the specific language governing permissions and -->
<!-- limitations under the License. -->

<!--
%% \VignetteEngine{knitr::rmarkdown}
%% \VignetteIndexEntry{GoogleGenomics Demo}
-->

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

Welcome to the GoogleGenomics workshop at *BioC 2015: Where Software and Biology Connect*

If you have not yet setup for Google Cloud Platform, please follow [these instructions](http://googlegenomics.readthedocs.org/en/latest/workshops/bioc-2015.html) to get setup and then come back to this vignette.

This workshop consists of four parts:

 * Part 1: Use the [GoogleGenomics](http://bioconductor.org/packages/devel/bioc/html/GoogleGenomics.html) package to work with Reads in Bioconductor
 * Part 2: Use the [GoogleGenomics](http://bioconductor.org/packages/devel/bioc/html/GoogleGenomics.html) package to work with Variants in Bioconductor
 * Part 3: Use the [bigrquery](http://cran.r-project.org/web/packages/bigrquery/index.html) package to analyze Variants via [Google BigQuery](https://cloud.google.com/bigquery/what-is-bigquery) 
 * Part 4: And then we bring it all together to do an end-to-end analysis!

Part 1: Work with Reads in Bioconductor
========================================

Open the code and the rendered vignette in separate windows:

* Open the vignette to run it line-by-line via:
```{r eval=FALSE}
file.edit(file.path(system.file(package = "GoogleGenomics"), "doc", "PlottingAlignments.Rmd"))
```

* View the rendered vignette 
```{r eval=FALSE}
file.show(file.path(system.file(package = "GoogleGenomics"), "doc", "PlottingAlignments.html"))
```

Alternatively, you can view the documentation for the [GoogleGenomics](http://bioconductor.org/packages/devel/bioc/html/GoogleGenomics.html) package by running `help(package="GoogleGenomics")` and clicking on *"User guides, package vignettes and other documentation."*.

Part 2: Work with Variants in Bioconductor
===========================================

Open the code and the rendered vignette in separate windows:

* Open the vignette to run it line-by-line via:
```{r eval=FALSE}
file.edit(file.path(system.file(package = "GoogleGenomics"), "doc", "AnnotateVariants.Rmd"))
```

* View the rendered vignette 
```{r eval=FALSE}
file.show(file.path(system.file(package = "GoogleGenomics"), "doc", "AnnotateVariants.html"))
```

Alternatively, you can view the documentation for the [GoogleGenomics](http://bioconductor.org/packages/devel/bioc/html/GoogleGenomics.html) package by running `help(package="GoogleGenomics")` and clicking on *"User guides, package vignettes and other documentation."*.


Part 3: Analyze Variants with BigQuery
======================================

Open the code and the rendered vignette in separate windows:

* Open the vignette to run it line-by-line via:
```{r eval=FALSE}
file.edit(file.path(system.file(package = "GoogleGenomicsBioc2015Workshop"), "doc", "BigQueryDemo.Rmd"))
```

* View the rendered vignette 
```{r eval=FALSE}
file.show(file.path(system.file(package = "GoogleGenomicsBioc2015Workshop"), "doc", "BigQueryDemo.html"))
```

Alternatively, you can view the documentation for the [GoogleGenomicsBioc2015Workshop](https://github.com/googlegenomics/bioconductor-workshop-r) package by running `help(package="GoogleGenomicsBioc2015Workshop")` and clicking on *"User guides, package vignettes and other documentation."*.

Part 4: Bring it all together in an end-to-end analysis
=======================================================

Open the code and the rendered vignette in separate windows:

* Open the vignette to run it line-by-line via:
```{r eval=FALSE}
file.edit(file.path(system.file(package = "GoogleGenomicsBioc2015Workshop"), "doc", "AllModalitiesDemo.Rmd"))
```

* View the rendered vignette 
```{r eval=FALSE}
file.show(file.path(system.file(package = "GoogleGenomicsBioc2015Workshop"), "doc", "AllModalitiesDemo.html"))
```

Alternatively, you can view the documentation for the [GoogleGenomicsBioc2015Workshop](https://github.com/googlegenomics/bioconductor-workshop-r) package by running `help(package="GoogleGenomicsBioc2015Workshop")` and clicking on *"User guides, package vignettes and other documentation."*.
